%----------------------------------------------------------------------------------------
% Bibliography
%----------------------------------------------------------------------------------------
\newpage % Includes a new page

% \pagenumbering{roman} % Changes page numbering to roman page numbers
%\bibliography{literature}

\section{References}

% \bibliography{literature.bib} % Add the filename of your bibliography
% \bibliographystyle{apsr} % Defines your bibliography style

% For citing, please see this sheet: http://merkel.texture.rocks/Latex/natbib.php



[1] Doll, T. (2013, February 12). Some Clarification is in Order: Average Speed by Position. Retrieved November 29, 2020, from \\ https://www.milehighreport.com/2013/2/12/3969128/some-clarification-is-in-order-average-speed-by-position \\
 
[2] Dudek, G., Jenkin, M. R., Milios, E., \& Wilkes, D. (1996). A taxonomy for multi-agent robotics. Autonomous Robots, 3(4), 375-397. \\
http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.57.621\&rep=rep1\&type=pdf \\
 
[3] Gaines, C. (2016, February 07). Cam Newton's emergence will change what quarterbacks look like in the NFL. Retrieved November 29, 2020, from \\ https://www.businessinsider.com/cam-newton-is-big-2016-2 \\
 
[4] Operations, N. (n.d.). Evolution of the NFL Player. Retrieved November 29, 2020, from \\ https://operations.nfl.com/the-players/evolution-of-the-nfl-player/ \\
 
[5] Platzer, A. (2010, August). Quantified differential dynamic logic for distributed hybrid systems. In International Workshop on Computer Science Logic (pp. 469-483). Springer, Berlin, Heidelberg.
\\ http://symbolaris.com/pub/QdL.pdf  \\
 
[6] Platzer A., Clarke E.M. (2009) Formal Verification of Curved Flight Collision Avoidance Maneuvers: A Case Study. In: Cavalcanti A., Dams D.R. (eds) FM 2009: Formal Methods. FM 2009. Lecture Notes in Computer Science, vol 5850. Springer, Berlin, Heidelberg. \\ https://doi.org/10.1007/978-3-642-05089-3\_35 \\
